Does motif participation provide unique information about species risk of extinction?

### 2021-09-29 manuscript/reorder_main_text.tex

    \subsubsection*{5) Persistence and network properties}
        $\Sigma$ and $\zeta$ for fixed effects, SC for random.

        Persistence is known to vary with global-scale and local-scale network properties.
        To correctly interpret any relationships between motifs and persistence, we must consider the context of these other relationships.
        To identify the relationship between global network structure and mean probability of persistence within a network, we fit a linear regression:
            \begin{equation}
                \Psi_{ik} \approx S_{i} + C_{i} + \pi_{disturbed_k} + S_{i}:C_{i} + S_{i}\pi_{disturbed_k} + C_{i}\pi_{disturbed_k} + S_{i}C_{i}\pi_{disturbed_k},
                \label{SCeq}
            \end{equation}
        where all symbols are as in equation~\ref{propreq}.
        As the three-way interaction was significant, we did not simplify the model.

        Persistence is also known to vary with local-scale measures of network structure. 
        To identify the relationships betwen local-scale properties and species' probabilities of persistence, we fit two more LMMs:

>>>>

    \subsubsection*{5) Persistence and network properties}

        Persistence is known to vary with global-scale and local-scale network properties.
        To correctly interpret any relationships between motifs and persistence, we must consider the context of these other relationships (Appendix \emph{S3.5}).
        To identify the relationship between global network structure and mean probability of persistence within a network, we fit a linear regression:

            \begin{equation}
                \Psi_{ik} \approx \Sigma_{i} + \zeta_{i} + \pi_{disturbed_k} + \Sigma_{i}:\zeta_{i} + \Sigma_{i}\pi_{disturbed_k} + \zeta_{i}\pi_{disturbed_k} + \Sigma_{i}\zeta_{i}\pi_{disturbed_k},
                \label{SCeq}
            \end{equation}

        where all symbols are as in equation~\ref{propreq} and~\ref{partic_SC}.
        As the three-way interaction was significant, we did not simplify the model.

        Persistence is also known to vary with local-scale measures of network structure. 
        To identify the relationships betwen local-scale properties and species' probabilities of persistence, we fit a final two LMMs:
